### 2023-10-31 chapters/paper_modelagnostic.tex
Fix margin violation

The ability to recognize when data are anomalous, i.e. if they originate from a distribution different from that of the training data, is a necessary property for machine learning models for safe and reliable applications in the real world. Historically, \textcite{bishop_novelty_1994} proposed to use a one-sided threshold on the log-likelihoods of a learned model as a decision rule to identify outliers in a dataset. However, recently, \textcite{nalisnick_deep_2019,hendrycks_deep_2019} showed that state-of-the-art deep generative models (DGMs) failed in this task, assigning higher a likelihood to out-of-distribution (OOD) data than in-distribution data. Most of the recent works focused on proposing new test statistics to alleviate the problem of using the plain likelihood, see \cref{sec_modelagnostic:related_works} for details.

>>>>

The ability to recognize when data are anomalous, i.e. if they originate from a distribution different from that of the training data, is a necessary property for machine learning models for safe and reliable applications in the real world. Historically, \textcite{bishop_novelty_1994} proposed to use a one-sided threshold on the log-likelihoods of a learned model as a decision rule to identify outliers in a dataset. However, recently, \textcite{nalisnick_deep_2019,hendrycks_deep_2019} showed that state-of-the-art deep generative models (DGMs) failed in this task, assigning higher a likelihood to out-of-distribution (OOD) data than in"-distribution data. Most of the recent works focused on proposing new test statistics to alleviate the problem of using the plain likelihood, see \cref{sec_modelagnostic:related_works} for details.
